Comparing Results with Mafessoni et al.

### 2019-07-10 LatexManuscript/legacy.tex
updated plot with variant count

A recent publication by Mafessoni et al. also identified a batch effect in the 1kGP using a method that uses linkage disequilibrium rather than quality metrics to identify nearly 20,000 suspicious variants \citep{mafessoni2018turning} (Figure \ref{Mafessoni_MutSpect}).
They identify 17,917 variants significantly associated to abnormal LD patterns that are not associated to $Q$ \ref{Mafessoni_MutSpect}.
We find that 3\% of the variants they identified are also in our list of suspicious variants and have correlated p-values to those identified using the GCAT method \ref{Mafessoni_MutSpect}.
We also find 23,172 $Q$-associated variants that are not associated to abnormal LD patterns. \sgcomment{Present proportions for both, or counts for both? Did they use only strict mask? }
Interestingly, the variants identified my Mafessoni et al. are not enriched in the mutational spectra described above (Figure \ref{Mafessoni_MutSpect}).
These results indicate that there may a multitude of batch effects in the 1kGP that can only be identified using a suite of association tests.

>>>>

A recent publication by Mafessoni et al. also identified a batch effect in the 1kGP using a method that uses linkage disequilibrium rather than quality metrics to identify 19,196 suspicious variants with 67\% of them passing the 1kGP strict mask \citep{mafessoni2018turning} (Figure \ref{Mafessoni_MutSpect}).
They identify 17,917 variants significantly associated to abnormal LD patterns that are not associated to $Q$ \ref{Mafessoni_MutSpect}.
We find that 1,279 ( 3\% ) of the variants they identified are also in our list of suspicious variants and have correlated p-values to those identified using the GCAT method \ref{Mafessoni_MutSpect}.
We also find 23,111 $Q$-associated variants that are not associated to abnormal LD patterns. 
Interestingly, the variants identified my Mafessoni et al. are not enriched in the mutational spectra described above (Figure \ref{Mafessoni_MutSpect}).
These results indicate that there may a multitude of batch effects in the 1kGP that can only be identified using a suite of association tests.

### 2019-07-10 PlottingScripts/ProcessedData/ScoopCheck.Rmd
updated plot with variant count

merged_regression_unmasked$strict_mask <- "Pass strict mask"
merged_regression_masked$strict_mask <- "Fail strict mask"

@@

print(paste("missing in Mafessoni (Fail): ",nrow(m_maf), "or : ", nrow(m_maf)/nrow(f)*100) )
print(paste("missing in ours (Fail): ",nrow(m_us), "or : ",nrow(m_us)/nrow(f)*100))
print(paste("present in both (Fail): ",nrow(both), "or : ",nrow(both)/nrow(f)*100))
print(paste("total (Fail): ", nrow(f)))
```

>>>>

merged_regression_unmasked$strict_mask <- paste0("Pass strict mask (",nrow(merged_regression_unmasked),")")
merged_regression_masked$strict_mask <- paste0("Fail strict mask (",nrow(merged_regression_masked),")")

@@

print(paste("missing in Mafessoni (Fail): ",nrow(m_maf), "or : ", nrow(m_maf)/nrow(f)*100) )
print(paste("missing in ours (Fail): ",nrow(m_us), "or : ",nrow(m_us)/nrow(f)*100))
print(paste("present in both (Fail): ",nrow(both), "or : ",nrow(both)/nrow(f)*100))
print(paste("total (Fail): ", nrow(f)))

m_maf <- to_plot %>%
           filter(pvalue_glm_filt == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- to_plot %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p < 2)

#present in both
both <- to_plot %>%
           filter(pvalue_glm_filt < 1 & Adjusted_Log10p > 2)

print(paste("missing in Mafessoni (total): ",nrow(m_maf), "or : ", nrow(m_maf)/nrow(to_plot)*100) )
print(paste("missing in ours (total): ",nrow(m_us), "or : ",nrow(m_us)/nrow(to_plot)*100))
print(paste("present in both (total): ",nrow(both), "or : ",nrow(both)/nrow(to_plot)*100))
print(paste("total (total): ", nrow(to_plot)))
```
